### 2022-05-14 manuscript.Rmd
Remove commented code

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior"),
  file_refit = brms_file_refit
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(
  res_prior,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm"),
  file_refit = brms_file_refit
)
summary(res_brm)
# plot(res_brm)

@@

# # Summarise fixed effects (incl. Bayes factors)
# describe_posterior(
#   res_brm,
#   centrality = "mean", ci = 0.95, ci_method = "ETI",
#   test = c("p_direction", "rope", "bayesfactor"),
#   rope_range = c(-0.1, 0.1)
# )

@@

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_reg"),
  file_refit = brms_file_refit
)
summary(res_prior_reg)
# plot(res_prior_reg)

# Run Bayesian multilevel model
res_brm_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_reg"),
  file_refit = brms_file_refit
)
summary(res_brm_reg)
# plot(res_brm_reg)

@@

# # Summarise fixed effects (incl. Bayes factors)
# describe_posterior(
#   res_brm_reg,
#   centrality = "mean", ci = 0.95, ci_method = "ETI",
#   test = c("p_direction", "rope", "bayesfactor"),
#   rope_range = c(-0.1, 0.1)
# )

@@

# Run prior predictive simulation
res_prior_gender <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_gender,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_gender"),
  file_refit = brms_file_refit
)
summary(res_prior_gender)
# plot(res_prior_gender)

# Run Bayesian multilevel model
res_brm_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_gender"),
  file_refit = brms_file_refit
)
summary(res_brm_gender)
# plot(res_brm_gender)

@@

# # Summarise fixed effects (incl. Bayes factors)
# describe_posterior(
#   res_brm_gender,
#   centrality = "mean", ci = 0.95, ci_method = "ETI",
#   test = c("p_direction", "rope", "bayesfactor"),
#   rope_range = c(-0.1, 0.1)
# )

>>>>

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior"),
  file_refit = brms_file_refit
)
summary(res_prior)

# Run Bayesian multilevel model
res_brm <- update(
  res_prior,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm"),
  file_refit = brms_file_refit
)
summary(res_brm)

@@

@@

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_reg"),
  file_refit = brms_file_refit
)
summary(res_prior_reg)

# Run Bayesian multilevel model
res_brm_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_reg"),
  file_refit = brms_file_refit
)
summary(res_brm_reg)

@@

@@

# Run prior predictive simulation
res_prior_gender <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_gender,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_gender"),
  file_refit = brms_file_refit
)
summary(res_prior_gender)

# Run Bayesian multilevel model
res_brm_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_gender"),
  file_refit = brms_file_refit
)
summary(res_brm_gender)

@@
